Cross-relaxation in dense ensembles of NV centers and application to magnetometry

### 2022-11-22 Talks/Soutenance 2022/presentation.tex
la tete a toto

\title{Low field depolarization of dense NV centers ensemble: application to magnetometry}
\author{Clément Pellet-Mary, Maxime Perdriat, Paul Huillery,\\ Gabriel Hétet}
\date{Nano-optics group}

@@

\begin{document}
\begin{frame}
\maketitle
\begin{center}
\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{logos}
\end{center}
\end{frame}
%\begin{frame}{Outline}
%\tableofcontents
%\end{frame}
%\section{Physics of the NV center}
%\begin{frame}{Preamble : the NV center}
%\centering
%\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide  NV properties}
%\end{frame}

\begin{frame}{Preamble : the 4 classes of NV centers}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide ODMR 4 classes}
\end{frame}

\begin{frame}{Context: Levitation of micro-diamonds in ion traps}
\centering
\includegraphics[width=0.9\textwidth,height=0.9\textheight,keepaspectratio]{Shema_meca}
\end{frame}

\begin{frame}{Context: Levitation of micro-diamonds in ion traps}
\centering
\includegraphics[width=0.9\textwidth,height=0.9\textheight,keepaspectratio]{Shema_meca_barre}
\end{frame}

@@

\section{Cross-relaxation with NV centers}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}
\begin{frame}{Principle of cross-relaxation with NV centers}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_CR_presentation}
\end{frame}

@@

\begin{frame}{Cross-relaxation between NV centers and NV centers}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_CR_adamas}
\end{frame}
\section{The NV-fluctuator model and experimental verification}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}
\begin{frame}{Presentation of the fluctuator model}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_fluct_intro}
\end{frame}

\begin{frame}{Predictions of the fluctuator model}
\begin{itemize}
\item $\Gamma_1$ increases when classes overlap spectrally (increase in the resonant fluctuator density).
\item The dipole induced depolarization has a stretched exponential profile:
$$ \rho_{00}(t) \propto \exp(-\sqrt{\frac{t}{T_1}})$$
\item The Fluctuators spectral response is broadened by their decay rate $\gamma_f$ (lifetime limit).
\end{itemize}
\end{frame}

\begin{frame}{$T_1$ measurement protocol}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_T1_protocol}
\end{frame}

@@

\begin{frame}{Competition between stretched and exponential decay}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_T1_exp_et_stretch}
\end{frame}

\begin{frame}{Spectral response of the fluctuators}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_fluct_linewidth}
\end{frame}

\begin{frame}{Geometry conditions for class resonances}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_geométries}
\end{frame}

\begin{frame}{PL mapping of the crystalline planes}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_carte}
\end{frame}

\begin{frame}{Limitations of the fluctuator model}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_limit_fluct}
\end{frame}

\section{Dipole-dipole interaction under low magnetic field}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}
\begin{frame}{Zero field depolarization sources (theory)}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_0B_theorie}
\end{frame}

@@

\section{Low field depolarization magnetometry (LFDM)}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}
\begin{frame}{Principle of LFDM}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_principle_LFDM}
\end{frame}

@@

\begin{frame}{Other applications}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_application_autre}
\end{frame}

\begin{frame}{Take home messages}
\begin{itemize}
\item The spin depolarization in dense NV ensemble is dominated by dipole-dipole interaction with fast decaying centers (fluctuators).
\medskip
\item The leading cause of depolarization in zero field is the spectral overlap of the NV classes, followed by the double flips.
\medskip
\item Low field depolarization magnetometry achieves a sensitivity $\sim 6\ \mu\rm T \cdot \mu \rm m^{3/2} / Hz^{1/2}$ with commercial samples.
\medskip
\item LFDM can be used with powder or polycristalline samples.
\end{itemize}

@@

%\begin{frame}
%\begin{tabularx}{0.9\textwidth}{X|l|l|l}
%{}&Traditional&GSLAC&LFDM\\
%\hline
%Microwave free&{}&{}&{} \\
%\hline
%Low magnetic field ($<$10 G)&{}&{}&{} \\
%\hline
%Robust to T and B inhomogeneities &{}&{}&{} \\
%\hline
%Orientation free &{}&{}&{} \\
%
%\end{tabularx}
%\end{frame}

>>>>

\title{Cross-relaxation in dense ensembles of NV centers and
application to magnetometry}
\author{Clément Pellet-Mary}
\date{PhD Defense}

@@

\begin{document}
\begin{frame}
\maketitle
%\begin{center}
%\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{logos}
%\end{center}
\end{frame}

\section{Sensing with quantum mechanics}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}

\begin{frame}{Quantum sensing and metrology}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_quantum_metrology}
\end{frame}

\begin{frame}{Magnetometry applications}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_example_magnetometry}
\end{frame}

\begin{frame}{Quantum magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_quantum_magnetometers}
\end{frame}

\section{Magnetometry with NV centers}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}

\begin{frame}{Colored centers in diamond}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide diamant}
\end{frame}

\begin{frame}{Synthetic diamond and NV centers}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_fab_sample}
\end{frame}

\begin{frame}{The NV center energy levels}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_NV_levels_1}
\end{frame}

\begin{frame}{The NV center energy levels}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_NV_levels}
\end{frame}

\begin{frame}{Optically detected magnetic resonance (ODMR)}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_ODMR_0}
\end{frame}

\begin{frame}{Experimental setup}
\centering
\includegraphics[width=0.9\textwidth,height=0.9\textheight,keepaspectratio]{Slide_setup}
\end{frame}

\begin{frame}{ODMR with NV ensemble}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_ODMR_8_classes}
\end{frame}

\begin{frame}{Sensitivity limit for NV ensemble magnetometry}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_NV_ensemble_sensi}
\end{frame}

\begin{frame}{Dipole-dipole interaction between two electronic spins}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_dipole_dipole}
\end{frame}

\begin{frame}{Interaction limit to NV ensemble magnetometry}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_interaction_limit}
\end{frame}

\section{Low field depolarization magnetometry (LFDM)}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}

@@

\begin{frame}{Pesentation of low field depolarization magnetometry (LFDM)}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_principle_LFDM}
\end{frame}

\section{Depolarization mechanisms in dense NV ensemble}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}
\begin{frame}{Principle of cross-relaxation with NV centers}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_CR_presentation}
\end{frame}

@@

\begin{frame}{Cross-relaxation between NV centers and NV centers}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_CR_adamas}
\end{frame}

\begin{frame}{Presentation of the fluctuator model}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_fluct_intro}
\end{frame}

@@

\begin{frame}{Zero field depolarization sources (theory)}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_0B_theorie}
\end{frame}

@@

@@

\begin{frame}{Conclusion}

@@

\begin{frame}{Acknowledgments}
